### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

Accordingly, if Definition~\ref{def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability can have at least $m$ bits of leakages. We can use the definition to detect those severe leakages. In the examples of Figure~\ref{fig:example1} and Figure~\ref{fig:example2}, because the input secret range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys. In Figure~\ref{fig:example1}, each item in the array could be read. Therefore, the channel capacity in Figure~\ref{fig:example1} is $\log_2{128} = \,7\, \mathrm{bits}$. In Figure~\ref{fig:example2}, there could be $4$ kinds of information, so the information leakages defined by channel capacity is $\log_2{4} = \,2\, \mathrm{bits}$. Compared with the result from Definition~\ref{chapter5:def}, we can see that the amount of leakages by Definition is a conservative estimation.

>>>>

Accordingly, if Definition~\ref{chapter5:def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability can have at least $m$ bits of leakages. We can use the definition to detect those severe leakages. In the examples of Figure~\ref{fig:example1} and Figure~\ref{fig:example2}, because the input secret range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys. In Figure~\ref{fig:example1}, each item in the array could be read. Therefore, the channel capacity in Figure~\ref{fig:example1} is $\log_2{128} = \,7\, \mathrm{bits}$. In Figure~\ref{fig:example2}, there could be $4$ kinds of information, so the information leakages defined by channel capacity is $\log_2{4} = \,2\, \mathrm{bits}$. Compared with the result from Definition~\ref{chapter5:def}, we can see that the amount of leakages by Definition is a conservative estimation.
